Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-13 Paper/ms.tex
Comment on kl divergence

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -217.65$. Nested Sampling also allows for calculation
of the ``information'', or Kullback-Leibler divergence from the prior to the
posterior, which quantifies how much we learned about the parameters:
\begin{eqnarray}
\mathcal{H} &=& \int p(\theta | D) \log\left[\frac{p(\theta | D)}{p(\theta)}\right] \, d\theta
\end{eqnarray}
An intuitive interpretation of this quantity is the number of times the
prior distribution had to be compressed by a factor of $e$ (if the logarithm
in the formula is a natural logarithm) to get to the posterior distribution.
For the $\nu$ Oph data the information was $\mathcal{H} \approx 77.7$ nats
(natural units) or 111 bits, so the posterior is roughly $e^{-77}$ times the
volume of the prior.

>>>>

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -217.65$. Nested Sampling also allows for calculation
of the ``information'', or Kullback-Leibler divergence (a quantity in information
theory) from the prior to the posterior, which quantifies how much we learned about the parameters:
\begin{eqnarray}
\mathcal{H} &=& \int p(\theta | D) \log\left[\frac{p(\theta | D)}{p(\theta)}\right] \, d\theta
\end{eqnarray}
An intuitive interpretation of this quantity is the number of times the
prior distribution had to be compressed by a factor of $e$ (if the logarithm
in the formula is a natural logarithm) to get to the posterior distribution.
For the $\nu$ Oph data the information was $\mathcal{H} \approx 77.7$ nats
(natural units) or 111 bits, so the posterior is roughly $e^{-77}$ times the
volume of the prior.
